Effective multi-body SU($N$)-symmetric interactions of ultracold fermionic atoms on a 3-D lattice

### 2019-02-27 multi_body_interactions/papers/theory/paper.tex
fixed error in multi-body thoery error concerned incorrect renormalization of third-order three-body loop diagrams

The effective two-body Hamiltonian in \eqref{eq:H_int_eff} has
contributions at all orders in the coupling constants, and can be
expanded in the form
\begin{align}
  H_2 = \shrink{
    \begin{tikzpicture}
      \begin{feynman}
        \vertex (v);
        \vertex[above left = of v] (f1);
        \vertex[below left = of v] (f2);
        \vertex[above right = of v] (f3);
        \vertex[below right = of v] (f4);
        \diagram* {
          (f1) -- (v),
          (f2) -- (v),
          (v) -- (f3),
          (v) -- (f4) };
      \end{feynman}
    \end{tikzpicture}}
  - \shrink{
    \begin{tikzpicture}
      \begin{feynman}
        \vertex (v1);
        \vertex[above left = of v1] (f1);
        \vertex[below left = of v1] (f2);
        \vertex[right = of v1] (v2);
        \vertex[above right = of v2] (f3);
        \vertex[below right = of v2] (f4);
        \diagram* {
          (f1) -- (v1),
          (f2) -- (v1),
          (v2) -- (f3),
          (v2) -- (f4),
          (v1) --[scalar, half left] (v2),
          (v1) --[scalar, half right] (v2) };
      \end{feynman}
    \end{tikzpicture}}
  + \shrink{
    \begin{tikzpicture}
      \begin{feynman}
        \vertex (v1);
        \vertex[above left = of v1] (f1);
        \vertex[below left = of v1] (f2);
        \vertex[right = of v1] (v2);
        \vertex[right = of v2] (v3);
        \vertex[above right = of v3] (f3);
        \vertex[below right = of v3] (f4);
        \diagram* {
          (f1) -- (v1),
          (f2) -- (v1),
          (v3) -- (f3),
          (v3) -- (f4),
          (v1)
          --[scalar, half left] (v2)
          --[scalar, half left] (v3),
          (v1)
          --[scalar, half right] (v2)
          --[scalar, half right] (v3) };
      \end{feynman}
    \end{tikzpicture}}
  + \cdots \equiv \shrink{
    \begin{tikzpicture}
      \begin{feynman}
        \vertex[blob] (v) {};
        \vertex[above left = of v] (f1);
        \vertex[below left = of v] (f2);
        \vertex[above right = of v] (f3);
        \vertex[below right = of v] (f4);
        \diagram* {
          (f1) -- (v),
          (f2) -- (v),
          (v) -- (f3),
          (v) -- (f4) };
      \end{feynman}
    \end{tikzpicture}},
  \label{eq:H_2_expansion}
\end{align}
where the blob on the right schematically represents the net effective
two-body interaction.  On physical grounds, the net two-body
interaction must clearly be finite, but individual sums over excited
states in the loop diagrams of \eqref{eq:H_2_expansion} may generally
diverge \cite{johnson2012effective}.  These divergences ultimately
appear due to our use of effective field theory to describe
inter-atomic interactions in \eqref{eq:H_int_start},
\eqref{eq:H_int_fields}, and \eqref{eq:H_int}, rather than a detailed
microscopic description of two-atom scattering.  Divergences of this
sort are a generic feature of field theories, and can be dealt with
using standard techniques such as renormalization.  We therefore
renormalize our coupling constants by introducing counter-terms
$\tilde G_X$ into the interaction Hamiltonian.

The introduction of counter-terms is merely a formal decomposition of
the ``bare'' coupling constants $G_X^{\t{bare}}$ that are used in
\eqref{eq:H_2_expansion} as $G_X^{\t{bare}} = G_X + \tilde G_X$.  In
performing such a decomposition, we are free to choose the values of
$G_X$, which in turn fixes the values of
$\tilde G_X \equiv G_X^{\t{bare}} - G_X$.  For convenience, we can
choose the values of $G_X$ to be those of the net effective coupling
constants on the right-hand side of \eqref{eq:H_2_expansion}.
Representing the new coupling constants $G_X$ by regular vertices and
the counter-terms $\tilde G_X$ by a crossed dot (i.e.~$\otimes$), this
choice leads to the {\it renormalization condition}
\begin{align}
  \substack{
    \shrink{
      \begin{tikzpicture}
        \begin{feynman}
          \vertex (v);
          \vertex[above left = of v] (f1);
          \vertex[below left = of v] (f2);
          \vertex[above right = of v] (f3);
          \vertex[below right = of v] (f4);
          \diagram* {
            (f1) -- (v),
            (f2) -- (v),
            (v) -- (f3),
            (v) -- (f4) };
        \end{feynman}
      \end{tikzpicture}}
    \\ \O(G)}
  + \substack{
    \shrink{
      \begin{tikzpicture}
        \begin{feynman}
          \vertex[crossed dot] (v) {};
          \vertex[above left = of v] (f1);
          \vertex[below left = of v] (f2);
          \vertex[above right = of v] (f3);
          \vertex[below right = of v] (f4);
          \diagram* {
            (f1) -- (v),
            (f2) -- (v),
            (v) -- (f3),
            (v) -- (f4) };
        \end{feynman}
      \end{tikzpicture}}
    \\ \O(\tilde G)}
  - \substack{
    \shrink{
      \begin{tikzpicture}
        \begin{feynman}
          \vertex (v1);
          \vertex[above left = of v1] (f1);
          \vertex[below left = of v1] (f2);
          \vertex[right = of v1] (v2);
          \vertex[above right = of v2] (f3);
          \vertex[below right = of v2] (f4);
          \diagram* {
            (f1) -- (v1),
            (f2) -- (v1),
            (v2) -- (f3),
            (v2) -- (f4),
            (v1) --[scalar, half left] (v2),
            (v1) --[scalar, half right] (v2) };
        \end{feynman}
      \end{tikzpicture}}
    \\ \O(G^2)}
  + \cdots = \substack{
    \shrink{
      \begin{tikzpicture}
        \begin{feynman}
          \vertex (v);
          \vertex[above left = of v] (f1);
          \vertex[below left = of v] (f2);
          \vertex[above right = of v] (f3);
          \vertex[below right = of v] (f4);
          \diagram* {
            (f1) -- (v),
            (f2) -- (v),
            (v) -- (f3),
            (v) -- (f4) };
        \end{feynman}
      \end{tikzpicture}}
    \\ \O(G)}.
  \label{eq:counter_term}
\end{align}
This renormalization condition has the benefit of allowing us to
express effective two-body interactions simply in terms of net
effective two-body coupling constants, rather than in terms of long
sums at all order of the bare coupling constants.  By construction,
the counter-terms we have introduced exactly cancel all terms beyond
leading order in \eqref{eq:H_2_expansion}, which implies that the
effective two-body interaction Hamiltonian is simply
\begin{align}
  H_2 = \shrink{
    \begin{tikzpicture}
      \begin{feynman}
        \vertex (v);
        \vertex[above left = of v] (f1);
        \vertex[below left = of v] (f2);
        \vertex[above right = of v] (f3);
        \vertex[below right = of v] (f4);
        \diagram* {
          (f1) -- (v),
          (f2) -- (v),
          (v) -- (f3),
          (v) -- (f4), };
      \end{feynman}
    \end{tikzpicture}}
  = \f12 \alpha_2^{(1)} \sum_{\abs{\set{\mu,\nu}}=2} G^{qr}_{st}
  \c_{\mu s}^\dag \c_{\nu t}^\dag \c_{\nu r} \c_{\mu q},
  \label{eq:H_2}
\end{align}
where for consistency with existing literature
\cite{johnson2012effective} we define $\alpha_2^{(1)} \equiv K$ as the
overlap integral between two atoms occupying non-interacting motional
ground states.

@@

Second, the renormalization condition in \eqref{eq:counter_term}
implies that the counter terms $\tilde G_X$ are second order in the
coupling constants $G_X$, i.e.~$\tilde G_X\sim G_X^2$.  Although the
effective Hamiltonian expansions in \eqref{eq:H_int_1_2} and
\eqref{eq:H_int_3} are organized in powers of the interaction
Hamiltonian $H_{\t{int}}$, the couplings $G_X$ are the ``small''
parameters in which we can formally organize a perturbation theory;
more specifically, the formally small quantities organizing our
perturbation theory are two-body ground-state interaction energies
(proportional to the couplings $G_X$) divided by the spectral gap of
the single-atom Hamiltonian $H_0$ (see Appendix
\ref{sec:pert_params}).  If $M$ atoms can only couple through terms
represented by a $p$-vertex diagrams for $p\ge p_M^{\t{min}}$, then
the leading order contribution to $M$-body interactions is order
$p_M^{\t{min}}$ in the couplings $G_X$.  If the same
$p_M^{\t{min}}$-vertex diagrams involve any counter-terms, however,
then these diagrams are at least order $p_M^{\t{min}}+1$ in the
couplings $G_X$.  Counter-terms therefore only appear at
next-to-leading order (NLO) in the calculation of effective $M$-body
interactions.

@@

  \propto K_n^2 \tilde G^{rs}_{r's'} G^{s't}_{s''t'}

@@

and its mirror image, where $\tilde G^{qr}_{st}$ is equal to the
counter-term associated with $G^{qr}_{st}$.  To leading order in the
coupling constants, the renormalization condition in
\eqref{eq:counter_term} implies that

@@

which means that the sum over all counter-term diagrams in
\eqref{eq:H_3_3_counter_term} is

@@

  \label{eq:H_3_3_counter_term_sum}
The net contribution of the these counter-term diagrams together with
the two-particle-loop diagrams in \eqref{eq:H_3_3_O} is therefore
  + \shrink{

@@

  = - \f12 \shrink{
  \label{eq:H_3_3_cancellation}

@@

An identical cancellation occurs for the mirror images of the diagrams
in \eqref{eq:H_3_3_O} and \eqref{eq:H_3_3_counter_term}, which results
in a contribution to the effective Hamiltonian that is equal to
\eqref{eq:H_3_3_cancellation}.  The contribution from the
three-particle-loop diagrams in \eqref{eq:H_3_3_S} is
The third-order three-body interaction Hamiltonian is therefore
  H_3^{(3)} &= \shrink{
          (f2) -- (v1) --[half right, scalar] (v2) -- (v3) -- (f5),
          (f2) -- (v1) --[half right] (v2) --[scalar] (v3) -- (f5),
    \end{tikzpicture}} \nonumber \\[1em]
  &= \p{\alpha_3^{(3)} - \alpha_5^{(3)}} \H_{3,1}^{(3)}
  - \p{\alpha_{4,3}^{(3)} + \alpha_5^{(3)}} \H_{3,2}^{(3)},
where, letting $E_{mn}\equiv E_m+E_n$,
  \alpha_3^{(3)} \equiv \sum_{\substack{\ell+m>0\\\ell+n>0}}

@@

  \label{eq:alph_3_3}

@@

Note that although \eqref{eq:H_3_3_S} is a loop diagram, the
associated factors $\alpha_3^{(3)}$ and $\alpha_5^{(3)}$ in
$H_3^{(3)}$ are finite.  At large $n$, atoms become free particles for
which $n$ essentially indexes discrete momentum states.  These atoms
thus have an energy which asymptotically scales as
The asymptotic behavior of $\alpha_3^{(3)}$ at large $\ell,m,n$ is
  \alpha_3^{(3)}
  \label{eq:alph_3_3_integral}
\item the integral expression in \eqref{eq:alph_3_3_integral} is a
  good approximation to the corresponding sum in \eqref{eq:alph_3_3}.
\eqref{eq:alph_3_3}, whose contribution to the value of
$\alpha_3^{(3)}$ is finite.  Convergence of $\alpha_5^{(3)}$ is

@@

  \c_{\sigma t} \c_{\rho s} \c_{\nu r} \c_{\mu q},

@@

  \c_{\sigma t} \c_{\rho s} \c_{\nu r} \c_{\mu q},

@@

and the mirror image of \eqref{eq:H_4_3_B}.  As we are computing the
leading-order contribution to effective four-body interactions, there
are no counter-terms contributions.  In principle, there is now also
the possibility to make the disconnected diagrams of the form

@@

Observing that the diagrams of the form in \eqref{eq:H_4_3_B} are
equal to their mirror image, the positive contributions to the
third-order four-body interaction Hamiltonian are

@@

  + \shrink{

@@

          (f3) -- (v2) --[scalar] (v3) -- (f7),
  + \shrink{

@@

  = 2 \shrink{
  + \shrink{

@@

while the negative contributions are
  \f12 \shrink{
  + \f12 \shrink{
          (f2) -- (v1) -- (v3) -- (f6),
          (f3) -- (v2) --[scalar] (v3) -- (f7),
  + \f12 \shrink{

@@

  + \f12 \shrink{

@@

  + \shrink{
such that the net third-order four-body interaction Hamiltonian is
  H_4^{(3)} &= 2 \shrink{
  + \shrink{
    \end{tikzpicture}} \nonumber \\
  &= \p{2\alpha_{4,1}^{(3)} - \alpha_5^{(3)}} \H_{4,1}^{(3)}
  + \p{\alpha_{4,2}^{(3)} - \alpha_5^{(3)}} \H_{4,2}^{(3)},

@@

  \c_{\sigma t} \c_{\rho s} \c_{\nu r} \c_{\mu q},

@@

>>>>

The effective two-body Hamiltonian in \eqref{eq:H_int_eff} has
contributions at all orders in the coupling constants, and can be
expanded in the form
\begin{align}
  H_2 = \shrink{
    \begin{tikzpicture}
      \begin{feynman}
        \vertex (v);
        \vertex[above left = of v] (f1);
        \vertex[below left = of v] (f2);
        \vertex[above right = of v] (f3);
        \vertex[below right = of v] (f4);
        \diagram* {
          (f1) -- (v),
          (f2) -- (v),
          (v) -- (f3),
          (v) -- (f4) };
      \end{feynman}
    \end{tikzpicture}}
  - \shrink{
    \begin{tikzpicture}
      \begin{feynman}
        \vertex (v1);
        \vertex[above left = of v1] (f1);
        \vertex[below left = of v1] (f2);
        \vertex[right = of v1] (v2);
        \vertex[above right = of v2] (f3);
        \vertex[below right = of v2] (f4);
        \diagram* {
          (f1) -- (v1),
          (f2) -- (v1),
          (v2) -- (f3),
          (v2) -- (f4),
          (v1) --[scalar, half left] (v2),
          (v1) --[scalar, half right] (v2) };
      \end{feynman}
    \end{tikzpicture}}
  + \shrink{
    \begin{tikzpicture}
      \begin{feynman}
        \vertex (v1);
        \vertex[above left = of v1] (f1);
        \vertex[below left = of v1] (f2);
        \vertex[right = of v1] (v2);
        \vertex[right = of v2] (v3);
        \vertex[above right = of v3] (f3);
        \vertex[below right = of v3] (f4);
        \diagram* {
          (f1) -- (v1),
          (f2) -- (v1),
          (v3) -- (f3),
          (v3) -- (f4),
          (v1)
          --[scalar, half left] (v2)
          --[scalar, half left] (v3),
          (v1)
          --[scalar, half right] (v2)
          --[scalar, half right] (v3) };
      \end{feynman}
    \end{tikzpicture}}
  + \cdots \equiv \shrink{
    \begin{tikzpicture}
      \begin{feynman}
        \vertex[blob] (v) {};
        \vertex[above left = of v] (f1);
        \vertex[below left = of v] (f2);
        \vertex[above right = of v] (f3);
        \vertex[below right = of v] (f4);
        \diagram* {
          (f1) -- (v),
          (f2) -- (v),
          (v) -- (f3),
          (v) -- (f4) };
      \end{feynman}
    \end{tikzpicture}},
  \label{eq:H_2_expansion}
\end{align}
where the blob on the right schematically represents the net effective
two-body interaction.  On physical grounds, the net two-body
interaction must clearly be finite, but individual sums over excited
states in the loop diagrams of \eqref{eq:H_2_expansion} may generally
diverge \cite{johnson2012effective}.  These divergences ultimately
appear due to our use of effective field theory to describe
inter-atomic interactions in \eqref{eq:H_int_start},
\eqref{eq:H_int_fields}, and \eqref{eq:H_int}, rather than a detailed
microscopic description of two-atom scattering.  Divergences of this
sort are a generic feature of field theories, and can be dealt with
using standard techniques such as renormalization.  We therefore
renormalize our coupling constants by introducing counter-terms
$\widetilde G_X$ into the interaction Hamiltonian.

The introduction of counter-terms is merely a formal decomposition of
the ``bare'' coupling constants $G_X^{\t{bare}}$ that are used in
\eqref{eq:H_2_expansion} as $G_X^{\t{bare}} = G_X + \widetilde G_X$.
In performing such a decomposition, we are free to choose the values
of $G_X$, which in turn fixes the values of
$\widetilde G_X \equiv G_X^{\t{bare}} - G_X$.  For convenience, we can
choose the values of $G_X$ to be those of the net effective coupling
constants on the right-hand side of \eqref{eq:H_2_expansion}.
Representing the new coupling constants $G_X$ by regular vertices and
the counter-terms $\widetilde G_X$ by a crossed dot (i.e.~$\otimes$),
this choice leads to the {\it renormalization condition}
  \substack{
    \\ \O(G)}
  + \substack{
    \\ \O(\widetilde G)}
  - \substack{
    \\ \O(G^2)}
  + \cdots = \substack{
    \\ \O(G)}.
  \label{eq:counter_term}
This renormalization condition has the benefit of allowing us to
express effective two-body interactions simply in terms of net
effective two-body coupling constants, rather than in terms of long
sums at all order of the bare coupling constants.  By construction,
the counter-terms we have introduced exactly cancel all terms beyond
leading order in \eqref{eq:H_2_expansion}, which implies that the
effective two-body interaction Hamiltonian is simply
  H_2 = \shrink{
  = \f12 \alpha_2^{(1)} \sum_{\abs{\set{\mu,\nu}}=2} G^{qr}_{st}
  \c_{\mu s}^\dag \c_{\nu t}^\dag \c_{\nu r} \c_{\mu q},
  \label{eq:H_2}
where for consistency with existing literature
\cite{johnson2012effective} we define $\alpha_2^{(1)} \equiv K$ as the
overlap integral between two atoms occupying non-interacting motional
ground states.

@@

Second, the renormalization condition in \eqref{eq:counter_term}
implies that the counter terms $\widetilde G_X$ are second order in
the coupling constants $G_X$, i.e.~$\widetilde G_X\sim G_X^2$.
Although the effective Hamiltonian expansions in \eqref{eq:H_int_1_2}
and \eqref{eq:H_int_3} are organized in powers of the interaction
Hamiltonian $H_{\t{int}}$, the couplings $G_X$ are the ``small''
parameters in which we can formally organize a perturbation theory;
more specifically, the formally small quantities organizing our
perturbation theory are two-body ground-state interaction energies
(proportional to the couplings $G_X$) divided by the spectral gap of
the single-atom Hamiltonian $H_0$ (see Appendix
\ref{sec:pert_params}).  If $M$ atoms can only couple through terms
represented by a $p$-vertex diagrams for $p\ge p_M^{\t{min}}$, then
the leading order contribution to $M$-body interactions is order
$p_M^{\t{min}}$ in the couplings $G_X$.  If the same
$p_M^{\t{min}}$-vertex diagrams involve any counter-terms, however,
then these diagrams are at least order $p_M^{\t{min}}+1$ in the
couplings $G_X$.  Counter-terms therefore only appear at
next-to-leading order (NLO) in the calculation of effective $M$-body
interactions.

@@

  \propto K_n^2 \widetilde G^{rs}_{r's'} G^{s't}_{s''t'}

@@

and its mirror image, where $\widetilde G^{qr}_{st}$ is equal to the
counter-term associated with $G^{qr}_{st}$.

The net contribution to the third-order three-body interaction
Hamiltonian from three-particle-loop diagrams of the form in
\eqref{eq:H_3_3_S} is
  = \p{\alpha_{3,1}^{(3)} - \alpha_5^{(3)}} \H_{3,1}^{(3)},
  \alpha_{3,1}^{(3)} \equiv \sum_{\substack{\ell+m>0\\\ell+n>0}}
  \label{eq:alph_3_3_1}
and
Even though this contribution comes from loop diagrams, the factors
$\alpha_{3,1}^{(3)}$ and $\alpha_5^{(3)}$ in \eqref{eq:alph_3_3_1} are
finite.  At large motional state indices $n$, atoms become free
particles for which $n$ essentially indexes discrete momentum states.
These atoms thus have an energy which asymptotically scales as
The asymptotic behavior of $\alpha_{3,1}^{(3)}$ at large $\ell,m,n$ is
  \alpha_{3,1}^{(3)}
  \label{eq:alph_3_3_1_integral}
\item the integral expression in \eqref{eq:alph_3_3_1_integral} is a
  good approximation to the corresponding sum in
  \eqref{eq:alph_3_3_1}.
\eqref{eq:alph_3_3_1}, whose contribution to the value of
$\alpha_{3,1}^{(3)}$ is finite.  Convergence of $\alpha_5^{(3)}$ is

The sum over loop diagrams in \eqref{eq:H_3_3_O}, meanwhile, contains
a divergence that must be cancelled out by the counter-terms in
\eqref{eq:H_3_3_counter_term}.  To leading order in the coupling
constants, the renormalization condition in \eqref{eq:counter_term}
implies that

@@

which can be expanded and solved explicitly for the counter-terms to
find
  \widetilde G^{rs}_{r''s''}
  = \sum_{\ell,m,r',s'} \f{K_{\ell m}^2}{K E_{\ell m}}
  G^{rs}_{r's'} G^{r's'}_{r''s''}.
In terms of ordinary coupling constants, the counter-term diagram in
\eqref{eq:H_3_3_counter_term} is therefore
      \vertex[above right = 4em of v1] (f3) {$\mu r''$};
      \vertex[above right = of v2] (f6) {$\nu s'''$};
        --[scalar, edge label=$n\nu s''$] (v2),
  = \sum_{\ell,m,r',s'}
  \f{K_{\ell m}^2 K_n^2}{K E_{\ell m} E_n}
Altogether, the contribution to the third-order three-body interaction
Hamiltonian from loop diagrams of the form in \eqref{eq:H_3_3_O} and
counter-term diagrams of the form in \eqref{eq:H_3_3_counter_term} is

@@

@@

  = \p{\alpha_{3,2}^{(3)} - \f12\alpha_{4,3}^{(3)} - \f12\alpha_5^{(3)}}
  \H_{3,2}^{(3)},

@@

  \alpha_{3,2}^{(3)}
  \equiv \sum_{\substack{\ell+m>0\\n>0}}
  \f{K_{\ell m} K_n}{E_{\ell m} E_n}
  \p{K^{\ell m}_n - \f{K_{\ell m} K_n}{K}},

@@

  \label{eq:alph_3_3_2}
and

@@

An equal contribution comes from the mirror images of these diagrams,
such that the net third-order three-body interaction Hamiltonian is
  H_3^{(3)} = \p{\alpha_{3,1}^{(3)} - \alpha_5^{(3)}} \H_{3,1}^{(3)}
  + \p{2\alpha_{3,2}^{(3)} - \alpha_{4,3}^{(3)} - \alpha_5^{(3)}}
  \H_{3,2}^{(3)}.
Note that the aforementioned divergence and its cancellation are
buried in $\alpha_{3,2}^{(3)}$.  Formally, this factor is calculated
by imposing an ultraviolet cutoff $\Lambda$ for the maximum values of
motional state indices $\ell,m,n$, and then taking the limit
$\Lambda\to\infty$.  This procedure ensures that $\alpha_{3,2}^{(3)}$
always remains finite.

@@

@@

  \c_{\sigma t} \c_{\rho s} \c_{\nu r} \c_{\mu q}

@@

and its mirror image, as well as
As we are computing the leading-order contribution to effective
four-body interactions, there are no counter-terms contributions.  In
principle, there is now also the possibility to make the disconnected
diagrams of the form

@@

The contribution to the third-order four-body interaction Hamiltonian
from diagrams of the form in \eqref{eq:H_4_3_B} is

@@

@@

  = \p{\alpha_{4,1}^{(3)} - \f12\alpha_5^{(3)}} \H_{4,1},
and
An equal contribution comes from the mirror images of these diagrams.
The contribution from diagrams of the form in \eqref{eq:H_4_3_C},
meanwhile, is

@@

@@

@@

@@

  = \p{\alpha_{4,2}^{(3)} - \alpha_5^{(3)}} \H_{4,2},

@@

and

@@

The net third-order four-body interaction Hamiltonian is therefore
  H_4^{(3)}
  = \p{2\alpha_{4,1}^{(3)} - \alpha_5^{(3)}} \H_{4,1}^{(3)}
  + \p{\alpha_{4,2}^{(3)} - \alpha_5^{(3)}} \H_{4,2}^{(3)}.
